### 2011-05-09 submitting.tex
some initial tries
git-svn-id: https://svn.mathsim.eu/documents/publications/journal/style@2675 a653633e-0a08-0410-9ecb-ed4064e9718a

% $Id$
\documentclass{ansarticle}
%
%
\title{Preparing and submitting articles for the Archive of Numerical
  Software}
\author[1]{Wolfgang Bangerth}
\author[2]{Peter Bastian}
\author[1]{Guido Kanschat\thanks{NSF}}
\author[3]{Michael Heroux}
\author[4]{Anders Logg}
\affil[1]{Department of Mathematics, Texas A\&M University}
\affil[2]{IWR, Universit\"at Heidelberg}
\affil[3]{Sandia National Laboratories}
\affil[4]{Simula, Oslo}
\begin{document}
\maketitle
\begin{abstract}
  This document describes the general structure of the
  \texttt{ansarticle} document class and serves as an example for its
  usage. \texttt{ansarticle.cls} is based on the standard \LaTeX{}
  \texttt{article.cls} as well as a few other standard packages. It
  fixes most style parameters to the preferred style of the Archive of
  Numerical Software.
\end{abstract}
\section{Implementation}
The file \texttt{ansarticle.cls} loads the standard LaTeX
\texttt{article.cls} and applies some changes to the layout.
\subsection{Requirements}
Upon loading, \texttt{ansarticle.cls} requires the following packages:
\begin{itemize}
\item \texttt{times} and \texttt{mathtpm} to use postscript fonts
\item \texttt{hyperref} in order to typeset hyper-links in the text
\item \texttt{fancyhdr} for page headers and footers
\item \texttt{authblk} for more convenient handling of author and
  affiliation lists
\item \texttt{listings} for source code listings
\end{itemize}
These packages are part of standard \TeX{} distributions.
\section{Usage}
\end{document}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2011-05-16 submitting.tex
Some initial work on LaTeX style files
git-svn-id: https://svn.mathsim.eu/documents/publications/journal/style@2679 a653633e-0a08-0410-9ecb-ed4064e9718a

@@
 \documentclass{ansarticle}
-%
-%
+
 \title{Preparing and submitting articles for the Archive of Numerical
@@
 \affil[4]{Simula, Oslo}
+\runningtitle{Preparing articles for ANS}
+\runningauthor{Bangerth, Bastian, Kanschat, Heroux, Logg}
+
 \begin{document}
+
 \maketitle
+
 \begin{abstract}
@@
 \end{abstract}
+
 \section{Implementation}
+
 The file \texttt{ansarticle.cls} loads the standard LaTeX
 \texttt{article.cls} and applies some changes to the layout.
+
 \subsection{Requirements}
+
+Test ccc $f(x) = u$
+
 Upon loading, \texttt{ansarticle.cls} requires the following packages:
+
 \begin{itemize}
-\item \texttt{times} and \texttt{mathtpm} to use postscript fonts
+\item \texttt{times} and \texttt{mathptm} to use postscript fonts
 \item \texttt{hyperref} in order to typeset hyper-links in the text
@@
 These packages are part of standard \TeX{} distributions.
+
 \section{Usage}
+
+Fill some pages so we see what it looks like:
+
+Lorem ipsum dolor sit amet, consectetur adipiscing elit. Maecenas
+vestibulum justo ut felis porttitor at egestas mauris varius. Etiam
+risus nibh, posuere vitae laoreet vitae, consectetur id risus. Vivamus
+adipiscing diam eget enim congue vel ultrices mi dignissim. Nullam
+volutpat, nunc eu ullamcorper tempus, eros orci rutrum enim, ac luctus
+nulla urna et felis. Sed auctor, dolor vel pellentesque tempus, magna
+tellus feugiat enim, nec rhoncus augue est sit amet nisl. Curabitur ac
+nisi eu orci porttitor egestas in sed tortor. Aliquam tincidunt orci
+vitae magna luctus eu gravida dolor hendrerit. Duis sit amet metus
+justo, vitae scelerisque neque. Nam vitae nisi eros. Curabitur
+convallis faucibus elit ut auctor. Morbi vel urna sit amet nisi
+pharetra laoreet. Maecenas vitae enim elit. Donec varius orci nisi, id
+blandit elit. Aliquam ornare pharetra ante, in porttitor erat mollis
+sed. Suspendisse potenti. Donec id tortor odio, et egestas
+eros. Aenean nec orci at diam porta tincidunt. Nam molestie tempus
+vestibulum. Praesent sed felis at est sodales elementum laoreet non
+risus. Nam urna augue, pulvinar et adipiscing vita
+e, auctor at sem.
+
+Lorem ipsum dolor sit amet, consectetur adipiscing elit. Maecenas
+vestibulum justo ut felis porttitor at egestas mauris varius. Etiam
+risus nibh, posuere vitae laoreet vitae, consectetur id risus. Vivamus
+adipiscing diam eget enim congue vel ultrices mi dignissim. Nullam
+volutpat, nunc eu ullamcorper tempus, eros orci rutrum enim, ac luctus
+nulla urna et felis. Sed auctor, dolor vel pellentesque tempus, magna
+tellus feugiat enim, nec rhoncus augue est sit amet nisl. Curabitur ac
+nisi eu orci porttitor egestas in sed tortor. Aliquam tincidunt orci
+vitae magna luctus eu gravida dolor hendrerit. Duis sit amet metus
+justo, vitae scelerisque neque. Nam vitae nisi eros. Curabitur
+convallis faucibus elit ut auctor. Morbi vel urna sit amet nisi
+pharetra laoreet. Maecenas vitae enim elit. Donec varius orci nisi, id
+blandit elit. Aliquam ornare pharetra ante, in porttitor erat mollis
+sed. Suspendisse potenti. Donec id tortor odio, et egestas
+eros. Aenean nec orci at diam porta tincidunt. Nam molestie tempus
+vestibulum. Praesent sed felis at est sodales elementum laoreet non
+risus. Nam urna augue, pulvinar et adipiscing vita
+e, auctor at sem.
+
+Lorem ipsum dolor sit amet, consectetur adipiscing elit. Maecenas
+vestibulum justo ut felis porttitor at egestas mauris varius. Etiam
+risus nibh, posuere vitae laoreet vitae, consectetur id risus. Vivamus
+adipiscing diam eget enim congue vel ultrices mi dignissim. Nullam
+volutpat, nunc eu ullamcorper tempus, eros orci rutrum enim, ac luctus
+nulla urna et felis. Sed auctor, dolor vel pellentesque tempus, magna
+tellus feugiat enim, nec rhoncus augue est sit amet nisl. Curabitur ac
+nisi eu orci porttitor egestas in sed tortor. Aliquam tincidunt orci
+vitae magna luctus eu gravida dolor hendrerit. Duis sit amet metus
+justo, vitae scelerisque neque. Nam vitae nisi eros. Curabitur
+convallis faucibus elit ut auctor. Morbi vel urna sit amet nisi
+pharetra laoreet. Maecenas vitae enim elit. Donec varius orci nisi, id
+blandit elit. Aliquam ornare pharetra ante, in porttitor erat mollis
+sed. Suspendisse potenti. Donec id tortor odio, et egestas
+eros. Aenean nec orci at diam porta tincidunt. Nam molestie tempus
+vestibulum. Praesent sed felis at est sodales elementum laoreet non
+risus. Nam urna augue, pulvinar et adipiscing vita
+e, auctor at sem.
+
+\section{Testing some math}
+
+Consider $f(x) = x^2$
+
+\section{Testing some code}
+
+\begin{c++}
+// Get dimensions of local mesh_data
+const uint num_local_cells = mesh_data.cell_vertices.size();
+assert(global_cell_indices.size() == num_local_cells);
+const uint num_cell_vertices = mesh_data.cell_vertices[0].size();
+
+// Build array of cell-vertex connectivity and partition vector
+std::vector<uint> cell_vertices;
+std::vector<uint> cell_vertices_partition;
+const uint size = num_local_cells*(num_cell_vertices + 1);
+cell_vertices.reserve(size);
+cell_vertices_partition.reserve(size);
+for (uint i = 0; i < num_local_cells; i++)
+{
+  cell_vertices.push_back(global_cell_indices[i]);
+  cell_vertices_partition.push_back(cell_partition[i]);
+  for (uint j = 0; j < num_cell_vertices; j++)
+  {
+    cell_vertices.push_back(mesh_data.cell_vertices[i][j]);
+    cell_vertices_partition.push_back(cell_partition[i]);
+  }
+}
+
+// Distribute cell-vertex connectivity
+MPI::distribute(cell_vertices, cell_vertices_partition);
+assert(cell_vertices.size());
+cell_vertices_partition.clear();
+\end{c++}
+
+\begin{python}
+# Time-stepping
+t = dt
+p = Progress("Time-stepping")
+while t < T + DOLFIN_EPS:
+
+    # Update pressure boundary condition
+    p_in.t = t
+
+    # Compute tentative velocity step
+    begin("Computing tentative velocity")
+    b1 = assemble(L1)
+    [bc.apply(A1, b1) for bc in bcu]
+    solve(A1, u1.vector(), b1, "gmres", "ilu")
+    end()
+
+    # Pressure correction
+    begin("Computing pressure correction")
+    b2 = assemble(L2)
+    [bc.apply(A2, b2) for bc in bcp]
+    solve(A2, p1.vector(), b2, "gmres", "amg_hypre")
+    end()
+
+    # Velocity correction
+    begin("Computing velocity correction")
+    b3 = assemble(L3)
+    [bc.apply(A3, b3) for bc in bcu]
+    solve(A3, u1.vector(), b3, "gmres", "ilu")
+    end()
+
+    # Plot solution
+    plot(p1, title="Pressure", rescale=True)
+    plot(u1, title="Velocity", rescale=True)
+
+    # Save to file
+    ufile << u1
+    pfile << p1
+
+    # Move to next time step
+    u0.assign(u1)
+    p.update(t / T)
+    t += dt
+\end{python}
+
 \end{document}

### 2011-05-16 submitting.tex
add bibliography
git-svn-id: https://svn.mathsim.eu/documents/publications/journal/style@2683 a653633e-0a08-0410-9ecb-ed4064e9718a

@@
 
-\section{Testing some code}
+\section{Code samples}
+
+All code listings are based on the \texttt{listings}
+package~\cite{HeinzMoses07}.  The style file \texttt{anslistings.sty},
+automatically included by \texttt{ansarticle.cls}, provides standard
+styles for a variety of common programming languages. Changing any
+listing style parameters is not encouraged and may lead to unexpected
+outcomes in the final publication.
+
+Below, we provide samples of listings for the languages available. If
+a language is missing, please contact the managing editor for an
+updated style file.
+
+\subsection{C++}
+
+C++ code should be compliant with the current C++ standard. Two
+commands are provided to prettyprint C++ code. First, an environment
+to put C++ code into the LaTeX file, namely
+
+\begin{latexcode}
+\begin{c++}
+  // Your C++ code here
+\end{c++}
+\end{latexcode}
+
+Alternatively, it is possible to use \lstinline[language=TeX]!\inputcpp{file.cc}!
+to print the C++ code in a file. Here is an example what C++ code
+looks like.
 
@@
 // Get dimensions of local mesh_data
-const uint num_local_cells = mesh_data.cell_vertices.size();
+const unsigned int num_local_cells = mesh_data.cell_vertices.size();
 assert(global_cell_indices.size() == num_local_cells);
-const uint num_cell_vertices = mesh_data.cell_vertices[0].size();
+const unsigned int num_cell_vertices = mesh_data.cell_vertices[0].size();
 
 // Build array of cell-vertex connectivity and partition vector
-std::vector<uint> cell_vertices;
-std::vector<uint> cell_vertices_partition;
-const uint size = num_local_cells*(num_cell_vertices + 1);
+std::vector<unsigned int> cell_vertices;
+std::vector<unsigned int> cell_vertices_partition;
+const unsigned int size = num_local_cells*(num_cell_vertices + 1);
 cell_vertices.reserve(size);
 cell_vertices_partition.reserve(size);
-for (uint i = 0; i < num_local_cells; i++)
+for (unsigned int i = 0; i < num_local_cells; i++)
 {
@@
   cell_vertices_partition.push_back(cell_partition[i]);
-  for (uint j = 0; j < num_cell_vertices; j++)
+  for (unsigned int j = 0; j < num_cell_vertices; j++)
   {
@@
 
+\subsection{Python}
 \begin{python}
@@
 
+\bibliographystyle{abbrv}
+\bibliography{submitting}
 \end{document}

### 2011-05-17 submitting.tex
adding and reformatting this and that
git-svn-id: https://svn.mathsim.eu/documents/publications/journal/style@2684 a653633e-0a08-0410-9ecb-ed4064e9718a

@@
 
-\title{Preparing and submitting articles for the Archive of Numerical
-  Software}
+\title{Preparing articles for submission to the\\
+  Archive of Numerical Software}
 \author[1]{Wolfgang Bangerth}
 \author[2]{Peter Bastian}
-\author[1]{Guido Kanschat\thanks{NSF}}
+\author[1]{Guido Kanschat\thanks{Additional thanks to my neighbor's dog
+  for waking me up on time to work on this style file}}
 \author[3]{Michael Heroux}
@@
 
-\section{Implementation}
+\section{Usage}
 
 The file \texttt{ansarticle.cls} loads the standard LaTeX
-\texttt{article.cls} and applies some changes to the layout.
+\texttt{article.cls} and some additional packages. It also sets up the
+layout. Hardly any of the options of the packages are available to the
+author, in order to keep the journal style consistent.
 
@@
 
-Test ccc $f(x) = u$
+Upon loading, \texttt{ansarticle.cls} requires the following packages:
 
-Upon loading, \texttt{ansarticle.cls} requires the following packages:
+% TODO: Anders, please update!
 
@@
 \end{itemize}
-These packages are part of standard \TeX{} distributions.
+These packages are part of standard \TeX{} distributions and should
+not cause any difficulties.
 
-\section{Usage}
+\subsection{Mathematical formul\ae}
 
-Fill some pages so we see what it looks like:
+We recommend using the \texttt{amsmath} package for setting
+mathematical formul\ae{}, and we guarantee compatibility with the
+\texttt{ansarticle} style.
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit. Maecenas
-vestibulum justo ut felis porttitor at egestas mauris varius. Etiam
-risus nibh, posuere vitae laoreet vitae, consectetur id risus. Vivamus
-adipiscing diam eget enim congue vel ultrices mi dignissim. Nullam
-volutpat, nunc eu ullamcorper tempus, eros orci rutrum enim, ac luctus
-nulla urna et felis. Sed auctor, dolor vel pellentesque tempus, magna
-tellus feugiat enim, nec rhoncus augue est sit amet nisl. Curabitur ac
-nisi eu orci porttitor egestas in sed tortor. Aliquam tincidunt orci
-vitae magna luctus eu gravida dolor hendrerit. Duis sit amet metus
-justo, vitae scelerisque neque. Nam vitae nisi eros. Curabitur
-convallis faucibus elit ut auctor. Morbi vel urna sit amet nisi
-pharetra laoreet. Maecenas vitae enim elit. Donec varius orci nisi, id
-blandit elit. Aliquam ornare pharetra ante, in porttitor erat mollis
-sed. Suspendisse potenti. Donec id tortor odio, et egestas
-eros. Aenean nec orci at diam porta tincidunt. Nam molestie tempus
-vestibulum. Praesent sed felis at est sodales elementum laoreet non
-risus. Nam urna augue, pulvinar et adipiscing vita
-e, auctor at sem.
+% TODO: [GK] What about math fonts
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit. Maecenas
-vestibulum justo ut felis porttitor at egestas mauris varius. Etiam
-risus nibh, posuere vitae laoreet vitae, consectetur id risus. Vivamus
-adipiscing diam eget enim congue vel ultrices mi dignissim. Nullam
-volutpat, nunc eu ullamcorper tempus, eros orci rutrum enim, ac luctus
-nulla urna et felis. Sed auctor, dolor vel pellentesque tempus, magna
-tellus feugiat enim, nec rhoncus augue est sit amet nisl. Curabitur ac
-nisi eu orci porttitor egestas in sed tortor. Aliquam tincidunt orci
-vitae magna luctus eu gravida dolor hendrerit. Duis sit amet metus
-justo, vitae scelerisque neque. Nam vitae nisi eros. Curabitur
-convallis faucibus elit ut auctor. Morbi vel urna sit amet nisi
-pharetra laoreet. Maecenas vitae enim elit. Donec varius orci nisi, id
-blandit elit. Aliquam ornare pharetra ante, in porttitor erat mollis
-sed. Suspendisse potenti. Donec id tortor odio, et egestas
-eros. Aenean nec orci at diam porta tincidunt. Nam molestie tempus
-vestibulum. Praesent sed felis at est sodales elementum laoreet non
-risus. Nam urna augue, pulvinar et adipiscing vita
-e, auctor at sem.
+\subsection{Supplementary material}
+Additional material, chich is not part of the article text, but part
+of the submission, for instance setup scripts or video output, can be
+linked from the article, using the \texttt{hyperref} commands
+(\texttt{hyperref} is automaticly included by
+\texttt{ansarticle}). URLs to such material should start with the
+filename. A suitable prefix will be added to the links in the
+editorial process.
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit. Maecenas
-vestibulum justo ut felis porttitor at egestas mauris varius. Etiam
-risus nibh, posuere vitae laoreet vitae, consectetur id risus. Vivamus
-adipiscing diam eget enim congue vel ultrices mi dignissim. Nullam
-volutpat, nunc eu ullamcorper tempus, eros orci rutrum enim, ac luctus
-nulla urna et felis. Sed auctor, dolor vel pellentesque tempus, magna
-tellus feugiat enim, nec rhoncus augue est sit amet nisl. Curabitur ac
-nisi eu orci porttitor egestas in sed tortor. Aliquam tincidunt orci
-vitae magna luctus eu gravida dolor hendrerit. Duis sit amet metus
-justo, vitae scelerisque neque. Nam vitae nisi eros. Curabitur
-convallis faucibus elit ut auctor. Morbi vel urna sit amet nisi
-pharetra laoreet. Maecenas vitae enim elit. Donec varius orci nisi, id
-blandit elit. Aliquam ornare pharetra ante, in porttitor erat mollis
-sed. Suspendisse potenti. Donec id tortor odio, et egestas
-eros. Aenean nec orci at diam porta tincidunt. Nam molestie tempus
-vestibulum. Praesent sed felis at est sodales elementum laoreet non
-risus. Nam urna augue, pulvinar et adipiscing vita
-e, auctor at sem.
-
-\section{Testing some math}
-
-Consider $f(x) = x^2$
-
-\section{Code samples}
+\subsection{Code samples}
 
@@
 
-\subsection{C++}
-
-C++ code should be compliant with the current C++ standard. Two
+\subsubsection{C++}
+code should be compliant with the current C++ standard. Two
 commands are provided to prettyprint C++ code. First, an environment
@@
 
-\subsection{Python}
+\subsubsection{Python}
+can be typeset as well.
+
 \begin{python}
@@
 
+\section{Production after article was accepted}
+\subsection{Publication metadata}
+
+Create a file \texttt{ansinfo.tex} in the same directory. The file
+contains macros defining the publication information like in the
+following listing:
+
+\inputlatex{ansinfo.tex}
+
+\section{Philosophi\ae{} Naturalis Principia Mathematica}
+
+Excerpt from~\cite{Newton87}.
+
+\subsection{Pr\ae{}fatio ad Lectorem}
+
+Cum Veteres Mechanicam (uti Author est Pappus) in verum Naturalium
+investigatione maximi fecerint, \& recentiores, missis formis
+substantialibus \& qualitatibus occultis, Ph\ae{}nomena Natur\ae{} ad leges
+Mathematicas revocare aggressi sint: Visum est in hoc Tractatu
+Mathesin excolere quatenus ea ad Philosophiam spectat. Mechanicam vero
+duplicem Veteres constituerunt: Rationalem qu\ae{} per Demonstrationes
+accurate procedit, \& Practicam. Ad practicam spectant Artes omnes
+Manuales, a quibus utiq; Mechanica nomen mutuata est. Cum autem
+Artifices parum accurate operari soleant, fit ut Mechanica omnis a
+Geometria ita distinguatur, ut quicquid accuratum sit ad Geometriam
+referatur, quicquid minus accuratum ad Mechanicam. Attamen errores non
+sunt Artis sed Artificum. Qui minus accurate operatur, imperfectior
+est Mechanicus, \& si quis accuratissime operari posset, hic foret
+Mechanicus omnium perfectissimus. Nam \& Linearum rectarum \& Circulorum
+descriptiones in quibus Geometria fundatur, ad Mechanicam
+pertinent. Has lineas describere Geometria non docet sed
+postulat. Postulat enim ut Tyro easdem accurate describere prius
+didicerit quam limen attingat Geometri\ae{}; dein, quomodo per has
+operationes Problemata solvantur, docet. Rectas \& circulos describere
+Problemata sunt sed non Geometrica. Ex Mechanica postulatur horum
+solutio, in Geometria docetur solutorum usus. Ac gloriatur Geometria
+quod tam paucis principiis aliunde petitis tam multa pr\ae{}stet. Fundatur
+igitur Geometria in praxi Mechanica, \& nihil aliud est quam Mechanic\ae{}
+universalis pars illa qu\ae{} artem mensurandi accurate proponit ac
+demonstrat. Cum autem artes Manuales in corporibus movendis pr\ae{}cipue
+versentur, fit ut Geometria ad magnitudinem, Mechanica ad motum vulgo
+reseratur. Quo sensu Mechanica rationalis erit Scientia Motuum qui ex
+viribus quibuscunq; resultant, \& virium qu\ae{} ad motus quoscunq;
+requiruntur, accurate proposita ac demonstrata. Pars h\ae{}c Mechanic\ae{} a
+Veteribus in Potentiis quinque ad artes manuales spectantibus exculta
+fuit, qui Gravitatem (cum potentia manualis non sit) vix aliter quam
+in ponderibus per potentias illas movendis considerarunt. Nos autem
+non Artibus sed Philosophi\ae{} consulentes, deq; potentiis non manualibus
+sed naturalibus scribentes, ea maxime tractamus qu\ae{} ad Gravitatem,
+levitatem, vim Elasticam, resistentiam Fluidorum \& ejusmodi vires seu
+attractivas seu impulsivas spectant: Et ea propter h\ae{}c nostra tanquam
+Philosophi\ae{} principia Mathematica proponimus. Omnis enim Philosophi\ae{}
+difficultas in eo versari videtur, ut a Ph\ae{}nomenis motuum investigemus
+vires Natur\ae{}, deinde ab his viribus demonstremus ph\ae{}nomena reliqua. Et
+hac spectant Propositiones generales quas Libro primo \& secundo
+pertractavimus. In Libro autem tertio exemplum hujus rei proposuimus
+per explicationem Systematis mundani. Ibi enim, ex ph\ae{}nomenis
+c\ae{}lestibus, per Propositiones in Libris prioribus Mathematice
+demonstratas, derivantur vires gravitatis quibus corpora ad Solem \&
+Planetas singulos tendunt. Deinde ex his viribus per Propositiones
+etiam Mathematicas deducuntur motus Planetarum, Cometarum, Lun\ae{} \&
+Maris. Utinam c\ae{}tera Natur\ae{} ph\ae{}nomena ex principiis Mechanicis eodem
+argumentandi genere derivare liceret. Nam multa me movent ut nonnihil
+suspicer ea omnia ex viribus quibusdam pendere posse, quibus corporum
+particul\ae{} per causas nondum cognitas vel in se mutuo impelluntur \&
+secundum figuras regulares coh\ae{}rent, vel ab invicem fugantur \&
+recedunt: quibus viribus ignotis, Philosophi hactenus Naturam frustra
+tentarunt. Spero autem quod vel huic Philosophandi modo, vel veriori
+alicui, Principia hic posita lucem aliquam pr\ae{}bebunt.
+
+In his edendis, Vir acutissimus \& in omni literarum genere
+eruditissimus Edmundus Halleius operam navavit, nec solum Typothetarum
+Sphalmata correxit \& Schemata incidi curavit, sed etiam Author fuit ut
+horum editionem aggrederer. Quippe cum demonstratam a me figuram
+Orbium c\ae{}lestium impetraverat, rogare non destitit ut eadem cum
+Societate Regali communicarem, Qu\ae{} deinde hortatibus \& benignis suis
+auspiciis effecit ut de eadem in lucem emittenda cogitare
+inciperem. At postquam Motuum Lunarium in\ae{}qualitates aggressus essem,
+deinde etiam alia tentare c\ae{}pissem qu\ae{} ad leges mensuras Gravitatis \&
+aliarum virium, ad figuras a corporibus secundum datas quascunque
+leges attractis describendas, ad motus corporum plurium inter se, ad
+motus corporum in Mediis resistentibus, ad vires, densitates \& motus
+Mediorum, ad Orbes Cometarum \& similia spectant, editionem in aliud
+tempus differendam esse putavi, ut c\ae{}tera rimarer \& una in publicum
+darem. Qu\ae{} ad motus Lunares spectant, (imperfecta cum sint,) in
+Corollariis Propositionis LXVI. simul complexus sum, ne singula
+methodo prolixiore quam pro rei dignitate proponere, \& sigillatim
+demonstrare tenerer, \& seriem reliquarum Propositionum
+interrumpere. Nonnulla sero inventa locis minus idoneis inserere
+malui, quam numerum Propositionum \& citationes mutare. Ut omnia
+candide legantur, \& defectus, in materia tam difficili non tam
+reprehendantur, quam novis Lectorum conatibus investigentur, \& benigne
+suppleantur, enixe rogo.
+
+\subsection{Definitiones}
+
+\subsubsection{Def. I}
+Quantitas Materi\ae{} est mensura ejusdem orta ex illius Densitate \&
+Magnitudine conjunctim.
+
+\paragraph{Aer}  duplo densior in duplo spatio quadruplus est. Idem
+intellige de Nive et Pulveribus per compressionem vel liquefactionem
+condensatis. Et par est ratio corporum omnium, qu\ae{} per causas
+quascunq; diversimode condensantur. Medii interea, si quod fuerit,
+interstitia partium libere pervadentis, hic nullam rationem
+habeo. Hanc autem quantitatem sub nomine corporis vel Mass\ae{} in
+sequentibus passim intelligo. Innotescit ea per corporis cujusq;
+pondus. Nam ponderi proportionalem esse reperi per experimenta
+pendulorum accuratissime instituta, uti posthac docebitur.
+
+\subsubsection{Def. II}
+Quantitas motus est mensura ejusdem orta ex Velocitate et quantitate
+Materi\ae{} conjunctim.
+
+\paragraph{Motus}
+totius est summa motuum in partibus singulis, adeoq; in corpore duplo
+majore \ae{}quali cum Velocitate duplus est, et dupla cum Velocitate
+quadruplus.
+
+\subsubsection{Def. III}
+Materi\ae{} vis insita est potentia resistendi, qua corpus unumquodq;,
+quantum in se est, perseverat in statu suo vel quiescendi vel movendi
+uniformiter in directum.
+
+\paragraph{H\ae{}c}
+semper proportionalis est suo corpori, neq; differt quicquam ab
+inertia Mass\ae{}, nisi in modo concipiendi. Per inertiam materi\ae{} fit ut
+corpus omne de statu suo vel quiescendi vel movendi difficulter
+deturbetur. Unde etiam vis insita nomine significantissimo vis inerti\ae{}
+dici possit. Exercet vero corpus hanc vim solummodo in mutatione
+status sui per vim aliam in se impressam facta, estq; exercitium ejus
+sub diverso respectu et Resistentia et Impetus: Resistentia quatenus
+corpus ad conservandum statum suum reluctatur vi impress\ae{}; Impetus
+quatenus corpus idem, vi resistentis obstaculi difficulter cedendo,
+conatur statum ejus mutare. Vulgus Resistentiam quiescentibus et
+Impetum moventibus tribuit; sed motus et quies, uti vulgo
+concipiuntur, respectu solo distinguuntur ab invicem, neq; semper vere
+quiescunt qu\ae{} vulgo tanquam quiescentia spectantur.
+
+\subparagraph{A subparagraph} If you really want to nest that deeply, go
+ahead! But, while you might have enjoyed
+reading~\cite{Wittgenstein21,Wittgenstein81}, you are encouraged to
+question the applicability to a publication on a thing as profane as
+software.
+
 \bibliographystyle{abbrv}

### 2011-05-27 paper.tex
Some more work on style file(s)
git-svn-id: https://svn.mathsim.eu/documents/publications/journal/style@2712 a653633e-0a08-0410-9ecb-ed4064e9718a

--- 2011-05-17 submitting.tex
@@
 
-\title{Preparing articles for submission to the\\
+\title{Preparing articles for submission to the \\
        Archive of Numerical Software}
@@
 \affil[3]{Sandia National Laboratories}
-\affil[4]{Simula, Oslo}
+\affil[4]{Simula Research Laboratory}
 \runningtitle{Preparing articles for ANS}
@@
 
+%------------------------------------------------------------------------------
 \begin{document}
@@
   usage. \texttt{ansarticle.cls} is based on the standard \LaTeX{}
-  \texttt{article.cls} as well as a few other standard packages. It
-  fixes most style parameters to the preferred style of the Archive of
-  Numerical Software.
+  \texttt{article.cls} and a few other standard packages. It fixes
+  style parameters to the preferred style of the Archive of Numerical
+  Software (ANS).
 \end{abstract}
 
-\section{Usage}
+%------------------------------------------------------------------------------
+\section{Requirements}
+
+To write an article for ANS, you need to download the following files
+from the ANS web page:
+\begin{itemize}
+\item
+  \emp{paper.tex}, the source file for this document and a template for
+  authors;
+\item
+  \emp{ansarticle.cls}, the ANS document class file;
+\item
+  \emp{anslistings.sty}, the ANS style file for typesetting of code;
+\item
+  \emp{bibliography.bib}, a bibliography with some important
+  references;
+\item
+  \emp{Makefile}, useful for building your document.
+\end{itemize}
 
@@
 
-\subsection{Requirements}
-
 Upon loading, \texttt{ansarticle.cls} requires the following packages:
-
-% TODO: Anders, please update!
-
-\begin{itemize}
-\item \texttt{times} and \texttt{mathptm} to use postscript fonts
-\item \texttt{hyperref} in order to typeset hyper-links in the text
-\item \texttt{fancyhdr} for page headers and footers
-\item \texttt{authblk} for more convenient handling of author and
-  affiliation lists
-\item \texttt{listings} for source code listings
-\end{itemize}
+\emp{a4wide},
+\emp{anslistings},
+\emp{algorithm},
+\emp{algorithmicx},
+\emp{amsmath},
+\emp{amssymb},
+\emp{booktabs},
+\emp{fancyhdr},
+\emp{graphicx},
+\emp{hyperref},
+\emp{authblk},
+\emp{lastpage},
+\emp{listings.}
 These packages are part of standard \TeX{} distributions and should
@@
 
-\subsection{Mathematical formul\ae}
+%------------------------------------------------------------------------------
+\section{Usage}
 
-We recommend using the \texttt{amsmath} package for setting
-mathematical formul\ae{}, and we guarantee compatibility with the
-\texttt{ansarticle} style.
+\subsection{Building the document}
 
-% TODO: [GK] What about math fonts
+Use this file (\emp{paper.tex}) as a template for your article. Then
+simply type \emp{make} to build your article. This will call
+\emp{pdflatex} to generate the PDF file \emp{paper.pdf}. To also call
+\emp{bibtex}, type \emp{make final}.
 
-\subsection{Supplementary material}
-Additional material, chich is not part of the article text, but part
-of the submission, for instance setup scripts or video output, can be
-linked from the article, using the \texttt{hyperref} commands
-(\texttt{hyperref} is automaticly included by
-\texttt{ansarticle}). URLs to such material should start with the
-filename. A suitable prefix will be added to the links in the
-editorial process.
+\subsection{Typesetting mathematical formul\ae}
 
-\subsection{Code samples}
+The ANS document class uses the amsmath and amssymb packages for
+improved typesetting of mathematical formul\ae like, e.g., this one:
+\begin{equation}
+  \cfrac{1}{\sqrt{2}+
+    \cfrac{1}{\sqrt{2}+
+      \cfrac{1}{\sqrt{2}+\dotsb
+  }}}.
+\end{equation}
+
+Make sure that you familiarize yourself with the \emp{amsmath}
+environments \emp{multline}, \emp{align} and \emp{split} (and know the
+differences between them). Avoid home-made splitting using
+\emp{\{array\}\{rcl\}}.
+
+\subsection{Typesetting tables}
+
+\fixme{Write something about typesetting tables with \emp{booktabs}.}
+
+\subsection{Typesetting code}
 
@@
 \subsubsection{C++}
-code should be compliant with the current C++ standard. Two
-commands are provided to prettyprint C++ code. First, an environment
-to put C++ code into the LaTeX file, namely
+
+Code should be compliant with the current C++ standard. Two commands
+are provided to prettyprint C++ code. First, an environment to put C++
+code into the LaTeX file, namely
+
+\fixme{Adjust width of code box, a little too wide now.}
 
@@
 
-Alternatively, it is possible to use \lstinline[language=TeX]!\inputcpp{file.cc}!
-to print the C++ code in a file. Here is an example what C++ code
-looks like.
+Alternatively, it is possible to use
+\lstinline[language=TeX]!\inputcpp{file.cc}!  to print the C++ code in
+a file. Here is an example what C++ code looks like.
 
@@
 
+\subsection{Handling supplementary material}
+
+Additional material, chich is not part of the article text, but part
+of the submission, for instance setup scripts or video output, can be
+linked from the article, using the \texttt{hyperref} commands
+(\texttt{hyperref} is automaticly included by
+\texttt{ansarticle}). URLs to such material should start with the
+filename. A suitable prefix will be added to the links in the
+editorial process.
+
+%------------------------------------------------------------------------------
 \section{Production after article was accepted}
@@
 
+%------------------------------------------------------------------------------
 \section{Philosophi\ae{} Naturalis Principia Mathematica}
 
-Excerpt from~\cite{Newton87}.
+Excerpt from~\cite{Newton1687}.
 
@@
 investigatione maximi fecerint, \& recentiores, missis formis
-substantialibus \& qualitatibus occultis, Ph\ae{}nomena Natur\ae{} ad leges
-Mathematicas revocare aggressi sint: Visum est in hoc Tractatu
+substantialibus \& qualitatibus occultis, Ph\ae{}nomena Natur\ae{} ad
+leges Mathematicas revocare aggressi sint: Visum est in hoc Tractatu
 Mathesin excolere quatenus ea ad Philosophiam spectat. Mechanicam vero
@@
 est Mechanicus, \& si quis accuratissime operari posset, hic foret
-Mechanicus omnium perfectissimus. Nam \& Linearum rectarum \& Circulorum
-descriptiones in quibus Geometria fundatur, ad Mechanicam
+Mechanicus omnium perfectissimus. Nam \& Linearum rectarum \&
+Circulorum descriptiones in quibus Geometria fundatur, ad Mechanicam
 pertinent. Has lineas describere Geometria non docet sed
@@
 solutio, in Geometria docetur solutorum usus. Ac gloriatur Geometria
-quod tam paucis principiis aliunde petitis tam multa pr\ae{}stet. Fundatur
-igitur Geometria in praxi Mechanica, \& nihil aliud est quam Mechanic\ae{}
-universalis pars illa qu\ae{} artem mensurandi accurate proponit ac
-demonstrat. Cum autem artes Manuales in corporibus movendis pr\ae{}cipue
-versentur, fit ut Geometria ad magnitudinem, Mechanica ad motum vulgo
-reseratur. Quo sensu Mechanica rationalis erit Scientia Motuum qui ex
-viribus quibuscunq; resultant, \& virium qu\ae{} ad motus quoscunq;
-requiruntur, accurate proposita ac demonstrata. Pars h\ae{}c Mechanic\ae{} a
-Veteribus in Potentiis quinque ad artes manuales spectantibus exculta
-fuit, qui Gravitatem (cum potentia manualis non sit) vix aliter quam
-in ponderibus per potentias illas movendis considerarunt. Nos autem
-non Artibus sed Philosophi\ae{} consulentes, deq; potentiis non manualibus
-sed naturalibus scribentes, ea maxime tractamus qu\ae{} ad Gravitatem,
+quod tam paucis principiis aliunde petitis tam multa
+pr\ae{}stet. Fundatur igitur Geometria in praxi Mechanica, \& nihil
+aliud est quam Mechanic\ae{} universalis pars illa qu\ae{} artem
+mensurandi accurate proponit ac demonstrat. Cum autem artes Manuales
+in corporibus movendis pr\ae{}cipue versentur, fit ut Geometria ad
+magnitudinem, Mechanica ad motum vulgo reseratur. Quo sensu Mechanica
+rationalis erit Scientia Motuum qui ex viribus quibuscunq; resultant,
+\& virium qu\ae{} ad motus quoscunq; requiruntur, accurate proposita
+ac demonstrata. Pars h\ae{}c Mechanic\ae{} a Veteribus in Potentiis
+quinque ad artes manuales spectantibus exculta fuit, qui Gravitatem
+(cum potentia manualis non sit) vix aliter quam in ponderibus per
+potentias illas movendis considerarunt. Nos autem non Artibus sed
+Philosophi\ae{} consulentes, deq; potentiis non manualibus sed
+naturalibus scribentes, ea maxime tractamus qu\ae{} ad Gravitatem,
 levitatem, vim Elasticam, resistentiam Fluidorum \& ejusmodi vires seu
-attractivas seu impulsivas spectant: Et ea propter h\ae{}c nostra tanquam
-Philosophi\ae{} principia Mathematica proponimus. Omnis enim Philosophi\ae{}
-difficultas in eo versari videtur, ut a Ph\ae{}nomenis motuum investigemus
-vires Natur\ae{}, deinde ab his viribus demonstremus ph\ae{}nomena reliqua. Et
-hac spectant Propositiones generales quas Libro primo \& secundo
-pertractavimus. In Libro autem tertio exemplum hujus rei proposuimus
-per explicationem Systematis mundani. Ibi enim, ex ph\ae{}nomenis
-c\ae{}lestibus, per Propositiones in Libris prioribus Mathematice
-demonstratas, derivantur vires gravitatis quibus corpora ad Solem \&
-Planetas singulos tendunt. Deinde ex his viribus per Propositiones
-etiam Mathematicas deducuntur motus Planetarum, Cometarum, Lun\ae{} \&
-Maris. Utinam c\ae{}tera Natur\ae{} ph\ae{}nomena ex principiis Mechanicis eodem
+attractivas seu impulsivas spectant: Et ea propter h\ae{}c nostra
+tanquam Philosophi\ae{} principia Mathematica proponimus. Omnis enim
+Philosophi\ae{} difficultas in eo versari videtur, ut a Ph\ae{}nomenis
+motuum investigemus vires Natur\ae{}, deinde ab his viribus
+demonstremus ph\ae{}nomena reliqua. Et hac spectant Propositiones
+generales quas Libro primo \& secundo pertractavimus. In Libro autem
+tertio exemplum hujus rei proposuimus per explicationem Systematis
+mundani. Ibi enim, ex ph\ae{}nomenis c\ae{}lestibus, per Propositiones
+in Libris prioribus Mathematice demonstratas, derivantur vires
+gravitatis quibus corpora ad Solem \& Planetas singulos
+tendunt. Deinde ex his viribus per Propositiones etiam Mathematicas
+deducuntur motus Planetarum, Cometarum, Lun\ae{} \& Maris. Utinam
+c\ae{}tera Natur\ae{} ph\ae{}nomena ex principiis Mechanicis eodem
 argumentandi genere derivare liceret. Nam multa me movent ut nonnihil
 suspicer ea omnia ex viribus quibusdam pendere posse, quibus corporum
-particul\ae{} per causas nondum cognitas vel in se mutuo impelluntur \&
-secundum figuras regulares coh\ae{}rent, vel ab invicem fugantur \&
+particul\ae{} per causas nondum cognitas vel in se mutuo impelluntur
+\& secundum figuras regulares coh\ae{}rent, vel ab invicem fugantur \&
 recedunt: quibus viribus ignotis, Philosophi hactenus Naturam frustra
@@
 \subsubsection{Def. I}
+
 Quantitas Materi\ae{} est mensura ejusdem orta ex illius Densitate \&

### 2011-06-03 paper.tex
More work on style file and instructions.
git-svn-id: https://svn.mathsim.eu/documents/publications/journal/style@2730 a653633e-0a08-0410-9ecb-ed4064e9718a

@@
 % $Id$
+
 \documentclass{ansarticle}
@@
 
+\fixme{Who should be listed as authors on this document?}
+
 \maketitle
@@
   This document describes the general structure of the
-  \texttt{ansarticle} document class and serves as an example for its
-  usage. \texttt{ansarticle.cls} is based on the standard \LaTeX{}
-  \texttt{article.cls} and a few other standard packages. It fixes
-  style parameters to the preferred style of the Archive of Numerical
-  Software (ANS).
+  \emp{ansarticle} document class and serves as an example for its
+  usage. The \emp{ansarticle} document class is based on the standard
+  \LaTeX{} \emp{article} document class and a few other standard
+  packages. It fixes style parameters to the preferred style of the
+  Archive of Numerical Software (ANS).
 \end{abstract}
@@
 \end{itemize}
+These files are all included in the tarball \emp{ansarticle.tar.gz}.
 
-The file \texttt{ansarticle.cls} loads the standard LaTeX
-\texttt{article.cls} and some additional packages. It also sets up the
+The file \emp{ansarticle.cls} loads the standard LaTeX
+\emp{article.cls} and some additional packages. It also sets up the
 layout. Hardly any of the options of the packages are available to the
@@
 
-Upon loading, \texttt{ansarticle.cls} requires the following packages:
+Upon loading, \emp{ansarticle.cls} requires the following packages:
 \emp{a4wide},
-\emp{anslistings},
-\emp{algorithm},
-\emp{algorithmicx},
-\emp{amsmath},
-\emp{amssymb},
+%\emp{anslistings},
+\emp{algorithm}, \emp{algorithmicx}, \emp{algpseudocode},
+\emp{authblk},
+\emp{amsmath}, \emp{amssymb},
 \emp{booktabs},
@@
 \emp{hyperref},
-\emp{authblk},
 \emp{lastpage},
-\emp{listings.}
-These packages are part of standard \TeX{} distributions and should
+\emp{listings},
+\emp{todonotes}.
+These packages are part of standard \LaTeX{} distributions and should
 not cause any difficulties.
@@
 
-The ANS document class uses the amsmath and amssymb packages for
-improved typesetting of mathematical formul\ae like, e.g., this one:
+The ANS document class uses the \emp{amsmath} and \emp{amssymb}
+packages for improved typesetting of mathematical formul\ae like,
+e.g., this one:
 \begin{equation}
@@
 differences between them). Avoid home-made splitting using
-\emp{\{array\}\{rcl\}}.
+\emp{\{array\}\{rcl\}}. For details, refer to the \emp{amsmath}
+documentation.
 
@@
 
-\fixme{Write something about typesetting tables with \emp{booktabs}.}
+Use the commands provided by the \emp{booktabs} package for better
+looking typesetting of tables, as illustrated in
+Table~\ref{tab:tableexample}.
+
+\begin{table}
+  \begin{center}
+    \begin{tabular}{lcc}
+      \toprule
+      Entity & Dimension & Codimension \\
+      \hline
+      Vertex & $0$ & $D$ \\
+      Edge & $1$ & $D-1$ \\
+      Face & $2$ & $D-2$ \\
+      & & \\
+      Facet & $D-1$ & $1$ \\
+      Cell & $D$ & $0$ \\
+      \bottomrule
+    \end{tabular}
+  \end{center}
+    \caption{Mesh entities and their dimensions/codimensions.}
+    \label{tab:tableexample}
+\end{table}
+
+\subsection{Typesetting algorithms}
+
+Use the functionality provided by the packages \emp{algorithm},
+\emp{algorithmic} and \emp{algpseudocode}, automatically included by
+the \emp{ansarticle} document class, to typeset algorithms. This is
+illustrated in Algorithm~\ref{alg:algorithmexample}.
+
+\begin{algorithm}
+  \begin{algorithmic}
+    \State $D^{0,0}(x,y) := 1$
+    \State $D^{1,0}(x,y) := \frac{1+2x+y}{2}$
+    \For{$p \gets 1$, $d-1$}
+    \State $D^{p+1,0}(x,y) := \left( \frac{2p+1}{p+1} \right)
+    \left( \frac{1 + 2x + y}{2} \right) D^{p,0}(x,y)
+    - \left( \frac{p}{p+1} \right) \left( \frac{1-y}{2} \right)^2
+    D^{p-1,0}(x,y)$
+    \EndFor
+    \For{$p \gets 0,d-1$}
+    \State $D^{p,1}(x,y) := D^{p,0}(x,y) \left( \frac{1+2p+(3+2p) y}{2} \right)$
+    \EndFor
+    \For{$p \gets 0,d-1$}
+    \For{$q \gets 1,d-p-1$}
+    \State $D^{p,q+1}(x,y) :=
+    \left( a_{q}^{2p+1,0} y + b_q^{2p+1,0} \right) D^{p,q}(x,y)
+    - c_q^{2p+1,0} D^{p,q-1}(x,y)$
+    \EndFor
+    \EndFor
+  \end{algorithmic}
+  \caption{Compute all triangular orthogonal polynomials up to degree
+    $d$ by recurrence}
+  \label{dubalg}
+\end{algorithm}
 
@@
 
-All code listings are based on the \texttt{listings}
-package~\cite{HeinzMoses07}. The style file \texttt{anslistings.sty},
-automatically included by \texttt{ansarticle.cls}, provides standard
-styles for a variety of common programming languages. Changing any
-listing style parameters is not encouraged and may lead to unexpected
-outcomes in the final publication.
+All code listings are based on the \emp{listings}
+package~\citep{HeinzMoses07}. The package \emp{anslistings},
+automatically included by \emp{ansarticle} document class, provides
+standard styles for a variety of common programming
+languages. Changing any style parameters for this package is not
+encouraged and may lead to unexpected outcomes in the final
+publication.
 
-Below, we provide samples of listings for the languages available. If
-a language is missing, please contact the managing editor for an
-updated style file.
+Below, we provide samples of listings for the some of the languages
+available. If a language is missing, please contact the managing
+editor for an updated style file.
 
@@
 code into the LaTeX file, namely
-
-\fixme{Adjust width of code box, a little too wide now.}
 
@@
 \lstinline[language=TeX]!\inputcpp{file.cc}!  to print the C++ code in
-a file. Here is an example what C++ code looks like.
+a file. Here is an example of typesetting of C++ code:
 
@@
 \subsubsection{Python}
-can be typeset as well.
+
+The following illustrates typesetting of Python code:
 
@@
 t = dt
-p = Progress("Time-stepping")
-while t < T + DOLFIN_EPS:
-
-    # Update pressure boundary condition
-    p_in.t = t
+while t < T:
 
     # Compute tentative velocity step
-    begin("Computing tentative velocity")
     b1 = assemble(L1)
@@
     solve(A1, u1.vector(), b1, "gmres", "ilu")
-    end()
 
     # Pressure correction
-    begin("Computing pressure correction")
     b2 = assemble(L2)
@@
     solve(A2, p1.vector(), b2, "gmres", "amg_hypre")
-    end()
 
     # Velocity correction
-    begin("Computing velocity correction")
     b3 = assemble(L3)
@@
     solve(A3, u1.vector(), b3, "gmres", "ilu")
-    end()
 
@@
     u0.assign(u1)
-    p.update(t / T)
     t += dt
@@
 
-Additional material, chich is not part of the article text, but part
-of the submission, for instance setup scripts or video output, can be
-linked from the article, using the \texttt{hyperref} commands
-(\texttt{hyperref} is automaticly included by
-\texttt{ansarticle}). URLs to such material should start with the
+Additional material which is not part of the article text, but part of
+the submission, for instance setup scripts or video output, can be
+linked from the article, using the \emp{hyperref} commands
+(\emp{hyperref} is automaticly included by
+\emp{ansarticle}). URLs to such material should start with the
 filename. A suitable prefix will be added to the links in the
 editorial process.
+
+\subsection{Citations}
+
+The \emp{ansarticle} document class imports the \emp{natbib} package,
+which provides the commands \emp{\textbackslash{}citet\{\}} and
+\emp{\textbackslash{}citep\{\}}. These should be used in place of the
+regular \emp{\textbackslash{}cite\{\}} command as illustrated by the
+following passage: It was found by \citet{Wittgenstein1921} that what
+we cannot speak about we must pass over in silence, contrary to common
+belief~\citep{Newton1687}.
+
+\subsection{Other}
+
+The \emp{ansarticle} document class provides a number of useful
+notation macros which you can find by browsing through the file
+\emp{ansarticle.cls}.
+
+\subsection{Checklist}
+
+\fixme{Add more things to this checklist!}
+
+Before submitting your manuscript to ANS, please review the following
+checklist:
+\begin{itemize}
+\item
+  Have you run a spell checker on your manuscript (using an American English
+  dictionary)?
+\item
+  Have you referred to all figures and tables (callouts)?
+\item
+  Have you used a scalable vector graphics format for all images where
+  possible?
+\end{itemize}
 
@@
 
-Create a file \texttt{ansinfo.tex} in the same directory. The file
+Create a file \emp{ansinfo.tex} in the same directory. The file
 contains macros defining the publication information like in the
@@
 
+\fixme{Should this section contain some more info?}
+
 %------------------------------------------------------------------------------
@@
 
-Excerpt from~\cite{Newton1687}.
+\fixme{Add missing references (Newton and Wittgenstein) to
+  bibliography.}
+
+\fixme{Also add main references for all libraries listed on the ANS
+  web page.}
+
+\fixme{Can we cut down some on the text here? It's pretty long.}
+
+Excerpt from~\citet{Newton1687}.
 
@@
 ahead! But, while you might have enjoyed
-reading~\cite{Wittgenstein21,Wittgenstein81}, you are encouraged to
+reading~\citet{Wittgenstein1921,Wittgenstein1981}, you are encouraged to
 question the applicability to a publication on a thing as profane as
@@
 \end{document}
-
-%%% Local Variables:
-%%% mode: latex
-%%% TeX-master: t
-%%% End:

### 2013-05-13 paper.tex
Some small fixes
git-svn-id: https://svn.mathsim.eu/documents/publications/journal/style@2731 a653633e-0a08-0410-9ecb-ed4064e9718a
misc changes
git-svn-id: https://svn.mathsim.eu/documents/publications/journal/style@3843 a653633e-0a08-0410-9ecb-ed4064e9718a
Remove introduction from Newton Fix bibstyle Add post acceptance procedures
git-svn-id: https://svn.mathsim.eu/documents/publications/journal/style@3995 a653633e-0a08-0410-9ecb-ed4064e9718a

@@
        Archive of Numerical Software}
-\author[1]{Wolfgang Bangerth}
-\author[2]{Peter Bastian}
-\author[1]{Guido Kanschat\thanks{Additional thanks to my neighbor's dog
+\author[1]{Editor O. Archive\thanks{Additional thanks to my neighbor's dog
   for waking me up on time to work on this style file}}
-\author[3]{Michael Heroux}
-\author[4]{Anders Logg}
-\affil[1]{Department of Mathematics, Texas A\&M University}
-\affil[2]{IWR, Universit\"at Heidelberg}
-\affil[3]{Sandia National Laboratories}
-\affil[4]{Simula Research Laboratory}
+\author[2]{Author O. Software}
+\affil[1]{The Archive of Numerical Software}
+\affil[2]{The Worlds Best Place for Numerical Software}
 \runningtitle{Preparing articles for ANS}
-\runningauthor{Bangerth, Bastian, Kanschat, Heroux, Logg}
+\runningauthor{Archive Editors}
 
@@
 \begin{document}
-
-\fixme{Who should be listed as authors on this document?}
 
@@
 \end{itemize}
-These files are all included in the tarball \emp{ansarticle.tar.gz}.
+These files are all included in the tarball \emp{ansarticle.tgz}.
 
@@
     $d$ by recurrence}
-  \label{dubalg}
+  \label{alg:algorithmexample}
 \end{algorithm}
@@
 
-\fixme{Add more things to this checklist!}
-
 Before submitting your manuscript to ANS, please review the following
 checklist:
-\begin{itemize}
+\begin{enumerate}
 \item
@@
   dictionary)?
+\item
+  Have you referenced all libraries you have been using and the
+  appropriate versions and descriptive publications?
 \item
@@
   possible?
-\end{itemize}
+\end{enumerate}
+
+Before submitting your source code to ANS, please review the following
+checklist:
+\begin{enumerate}
+\item Does a simple 'make' or similar build and run the program in a
+  default configuration?
+\item Did you include all configuration information necessary?
+\item Did you include instructions on how to reproduce the examples in
+  the text?
+\end{enumerate}
 
@@
 \section{Production after article was accepted}
-\subsection{Publication metadata}
 
-Create a file \emp{ansinfo.tex} in the same directory. The file
-contains macros defining the publication information like in the
-following listing:
+\subsection{The manuscript}
+
+Once the article is accepted, the editor will send you a file
+\emp{ansinfo.tex} in the same directory. The file contains macros
+defining the publication information like in the following listing:
 
@@
 
-\fixme{Should this section contain some more info?}
+Please copy this file where \LaTeX{} can find it and recompile your
+manuscript to produce the finale version of the PDF.
+
+\subsection{The source code}
+
+If necessary, clean up the source code directory. Make sure you
+include only the files readers should download with the source (see
+the next subsection on media files). Make sure, a simple 'make' or
+similar will run a first example. Assert that the data in the
+manuscript can be reproduced.
+
+\subsection{The media directory}
+
+Every article comes with a media directory. This directory contains a
+file \texttt{index.html} which is linked from the article page and
+should serve as an entry point to your media files. The minimum
+requirement on this file is the following head:
+
+\begin{lstlisting}[language=html]
+<!DOCTYPE html PUBLIC "-//W3C//DTD XHTML 1.0 Transitional//EN"
+"http://www.w3.org/TR/xhtml1/DTD/xhtml1-transitional.dtd">
+
+<html xmlns="http://www.w3.org/1999/xhtml">
+
+<head>
+  <title>ANS V(N) Authors: Title</title>
+  <link rel="stylesheet" type="text/css" href="/ans.css"/>
+</head>
+
+<body>
+  <h2>Archive of Numerical Software V(N)</h2>
+  <h1>Title</h1>
+  <h2>Authors</h2>
+
+  Text and links
+</body>
+</html>
+\end{lstlisting}
+
+The occurences of \lstinline[language=html]!V(N)! should be replaced
+by the assigned volume and number of the publication,
+\lstinline[language=html]!Title! and
+\lstinline[language=html]!Authors! accordingly.  You are welcome to
+use image tags in this file.
+
+Add your image files and movies to this directory, not to the source
+code!
 
@@
 
-\fixme{Add missing references (Newton and Wittgenstein) to
-  bibliography.}
-
 \fixme{Also add main references for all libraries listed on the ANS
@@
 
-\fixme{Can we cut down some on the text here? It's pretty long.}
-
-Excerpt from~\citet{Newton1687}.
-
-\subsection{Pr\ae{}fatio ad Lectorem}
-
-Cum Veteres Mechanicam (uti Author est Pappus) in verum Naturalium
-investigatione maximi fecerint, \& recentiores, missis formis
-substantialibus \& qualitatibus occultis, Ph\ae{}nomena Natur\ae{} ad
-leges Mathematicas revocare aggressi sint: Visum est in hoc Tractatu
-Mathesin excolere quatenus ea ad Philosophiam spectat. Mechanicam vero
-duplicem Veteres constituerunt: Rationalem qu\ae{} per Demonstrationes
-accurate procedit, \& Practicam. Ad practicam spectant Artes omnes
-Manuales, a quibus utiq; Mechanica nomen mutuata est. Cum autem
-Artifices parum accurate operari soleant, fit ut Mechanica omnis a
-Geometria ita distinguatur, ut quicquid accuratum sit ad Geometriam
-referatur, quicquid minus accuratum ad Mechanicam. Attamen errores non
-sunt Artis sed Artificum. Qui minus accurate operatur, imperfectior
-est Mechanicus, \& si quis accuratissime operari posset, hic foret
-Mechanicus omnium perfectissimus. Nam \& Linearum rectarum \&
-Circulorum descriptiones in quibus Geometria fundatur, ad Mechanicam
-pertinent. Has lineas describere Geometria non docet sed
-postulat. Postulat enim ut Tyro easdem accurate describere prius
-didicerit quam limen attingat Geometri\ae{}; dein, quomodo per has
-operationes Problemata solvantur, docet. Rectas \& circulos describere
-Problemata sunt sed non Geometrica. Ex Mechanica postulatur horum
-solutio, in Geometria docetur solutorum usus. Ac gloriatur Geometria
-quod tam paucis principiis aliunde petitis tam multa
-pr\ae{}stet. Fundatur igitur Geometria in praxi Mechanica, \& nihil
-aliud est quam Mechanic\ae{} universalis pars illa qu\ae{} artem
-mensurandi accurate proponit ac demonstrat. Cum autem artes Manuales
-in corporibus movendis pr\ae{}cipue versentur, fit ut Geometria ad
-magnitudinem, Mechanica ad motum vulgo reseratur. Quo sensu Mechanica
-rationalis erit Scientia Motuum qui ex viribus quibuscunq; resultant,
-\& virium qu\ae{} ad motus quoscunq; requiruntur, accurate proposita
-ac demonstrata. Pars h\ae{}c Mechanic\ae{} a Veteribus in Potentiis
-quinque ad artes manuales spectantibus exculta fuit, qui Gravitatem
-(cum potentia manualis non sit) vix aliter quam in ponderibus per
-potentias illas movendis considerarunt. Nos autem non Artibus sed
-Philosophi\ae{} consulentes, deq; potentiis non manualibus sed
-naturalibus scribentes, ea maxime tractamus qu\ae{} ad Gravitatem,
-levitatem, vim Elasticam, resistentiam Fluidorum \& ejusmodi vires seu
-attractivas seu impulsivas spectant: Et ea propter h\ae{}c nostra
-tanquam Philosophi\ae{} principia Mathematica proponimus. Omnis enim
-Philosophi\ae{} difficultas in eo versari videtur, ut a Ph\ae{}nomenis
-motuum investigemus vires Natur\ae{}, deinde ab his viribus
-demonstremus ph\ae{}nomena reliqua. Et hac spectant Propositiones
-generales quas Libro primo \& secundo pertractavimus. In Libro autem
-tertio exemplum hujus rei proposuimus per explicationem Systematis
-mundani. Ibi enim, ex ph\ae{}nomenis c\ae{}lestibus, per Propositiones
-in Libris prioribus Mathematice demonstratas, derivantur vires
-gravitatis quibus corpora ad Solem \& Planetas singulos
-tendunt. Deinde ex his viribus per Propositiones etiam Mathematicas
-deducuntur motus Planetarum, Cometarum, Lun\ae{} \& Maris. Utinam
-c\ae{}tera Natur\ae{} ph\ae{}nomena ex principiis Mechanicis eodem
-argumentandi genere derivare liceret. Nam multa me movent ut nonnihil
-suspicer ea omnia ex viribus quibusdam pendere posse, quibus corporum
-particul\ae{} per causas nondum cognitas vel in se mutuo impelluntur
-\& secundum figuras regulares coh\ae{}rent, vel ab invicem fugantur \&
-recedunt: quibus viribus ignotis, Philosophi hactenus Naturam frustra
-tentarunt. Spero autem quod vel huic Philosophandi modo, vel veriori
-alicui, Principia hic posita lucem aliquam pr\ae{}bebunt.
-
-In his edendis, Vir acutissimus \& in omni literarum genere
-eruditissimus Edmundus Halleius operam navavit, nec solum Typothetarum
-Sphalmata correxit \& Schemata incidi curavit, sed etiam Author fuit ut
-horum editionem aggrederer. Quippe cum demonstratam a me figuram
-Orbium c\ae{}lestium impetraverat, rogare non destitit ut eadem cum
-Societate Regali communicarem, Qu\ae{} deinde hortatibus \& benignis suis
-auspiciis effecit ut de eadem in lucem emittenda cogitare
-inciperem. At postquam Motuum Lunarium in\ae{}qualitates aggressus essem,
-deinde etiam alia tentare c\ae{}pissem qu\ae{} ad leges mensuras Gravitatis \&
-aliarum virium, ad figuras a corporibus secundum datas quascunque
-leges attractis describendas, ad motus corporum plurium inter se, ad
-motus corporum in Mediis resistentibus, ad vires, densitates \& motus
-Mediorum, ad Orbes Cometarum \& similia spectant, editionem in aliud
-tempus differendam esse putavi, ut c\ae{}tera rimarer \& una in publicum
-darem. Qu\ae{} ad motus Lunares spectant, (imperfecta cum sint,) in
-Corollariis Propositionis LXVI. simul complexus sum, ne singula
-methodo prolixiore quam pro rei dignitate proponere, \& sigillatim
-demonstrare tenerer, \& seriem reliquarum Propositionum
-interrumpere. Nonnulla sero inventa locis minus idoneis inserere
-malui, quam numerum Propositionum \& citationes mutare. Ut omnia
-candide legantur, \& defectus, in materia tam difficili non tam
-reprehendantur, quam novis Lectorum conatibus investigentur, \& benigne
-suppleantur, enixe rogo.
+As an example text, we present an excerpt from~\citet{Newton1687}.
 
@@
 
-\bibliographystyle{abbrv}
+\bibliographystyle{abbrvnat}
 \bibliography{submitting}
